Untitled

### 2022-07-07 Main_Figures/Figure3.Rmd
edit

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + 
geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
coord_cartesian(ylim=c(1,100),clip="off") + 
ylab("Number of visits") +  
theme_ms() + 
theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids")) +
scale_y_log10() +
ggtitle(NULL, subtitle = "(d)") +
annotate(geom = "text", x = -1.7, y =0.2 , label = "High flower N.", size = 8) +
annotate(geom = "text", x = -1.7, y =0.12 , label = "Small flowers", size = 8) + 
annotate(geom = "text", x = 1.8, y =0.2 , label = "Low flower N.", size = 8) + 
annotate(geom = "text", x = 1.8, y =0.12 , label = "Large flowers", size = 8) +
xlab("") +
annotate(geom = "text", x = -0.1, y =0.35 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + xlab("") + theme(panel.border=element_rect(color="black",size=1.2))

>>>>

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + 
geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
coord_cartesian(ylim=c(1,100),clip="off") + 
ylab("Number of visits") +  
theme_ms() + 
theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids")) +
scale_y_log10() +
ggtitle(NULL, subtitle = "(d)") +
annotate(geom = "text", x = -1.7, y =0.2 , label = "High flower N.", size = 8) +
annotate(geom = "text", x = -1.75, y =0.12 , label = "Small flowers", size = 8) + 
annotate(geom = "text", x = 1.8, y =0.2 , label = "Low flower N.", size = 8) + 
annotate(geom = "text", x = 1.8, y =0.12 , label = "Large flowers", size = 8) +
xlab("") +
annotate(geom = "text", x = -0.1, y =0.35 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + xlab("") + theme(panel.border=element_rect(color="black",size=1.2))

### 2022-07-07 Manuscript/Lanuza_et_al_2022.Rmd
edit

  plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Pollinator dependence - floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Pollinator dependence - floral display axis")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - flower size axis")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - flower size axis")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
    xlab("Flower number - flower size axis") +
    ylab("Pollinator dependence - floral display axis")

@@

The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits [@salguero2016]. Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds. However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances [@bartomeus2016], to better capture the strength of these mutualistic interactions at a macroecological scale.

We provide solid evidence for the generality of several hypothesized trait associations across a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and linked the reproductive spectrum with previously described fast-slow continuum' life-history strategies in plants [@salguero2016] and animals [@healy2019], as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan. For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach. We found support to this trait association and show that other life history traits also covariate along this axis. Our study also complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers [are concentrated in the trait space](no pillo esto) and are associated with woody life forms with high flower number. Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors. Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays. Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.

Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales. For example, as predicted by [evolutionary? life-history?]() theory, larger investments floral size and rewards to attract pollinators makes sense when pollinator dependence is higher, but this might trade off with the resources allocated to ovule production [mirate la literatura de esto... seguro que hay papers. Además, si esto que digo l apoyan los datos, puede ser algo que la gente querra citar (YO QUIEREO!) asi que dejalo explicito](Anne Leonard tenia algo de eso, creo).  Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings [@hegland2005; @lazaro2013; @kaiser2014]. Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020]. For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies [name which ones]() and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies. In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.

>>>>

  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Pollinator dependence - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Pollinator dependence - Floral display axis")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - Flower size axis")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - Flower size axis")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
    xlab("Flower number - Flower size axis") +
    ylab("Pollinator dependence - Floral display axis")

@@

The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits [@diaz2016; @carmona2021], our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits [@salguero2016]. Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds. However, they were insufficient to capture the visitation rates by guild or other species-level network metrics, which highlight the need to account for other local factors, such as species relative abuncances [@bartomeus2016], to better understand the association of these mutualistic interactions at a macroecological scale.

Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan. For instance, although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach. We found support to this trait association and show that other life history traits also covariate along this axis. Our study also complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are associated with woody life forms with high flower number. Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors. Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays. Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.

Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales. For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014]. As predicted by evolutionary life-history theory [@stebbins1970], larger investments on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher but there are compromises (as the flower number - floral display) that can affect the reproductive investment to other organs such as ovule number and affect pollen transfer and seed production

However, the investment in floral display has evident compromises between flower number and flower size

there are evident compromises as the one showed between flower number and flower size that affect the reproductive investment in ovules and pollen transfer as also shown for other wind pollinated species [@friedman2011]

  By combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings [@hegland2005; @lazaro2013; @kaiser2014]. Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020]. For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies [name which ones]() and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies. In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.

### 2022-07-07 Manuscript/Lanuza_et_al_2022.tex
edit

The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03). Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization. On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a). However, specialization showed the opposite trend on this axis (figure S9g). On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c). Again, specialization showed the opposite trend to number of visits (figure S9i). \href{}{crees que podemos meter una figura de este resultado en main text? Si no esta ahi, no lo va a ver nadie}

@@

The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence \href{}{que opinas de que pol dep salga en dos ejes? No es raro?}. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{16},\protect\hyperlink{ref-carmona2021}{18}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}. Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds. However, they were insufficient to capture the visitation rates, which highlight the need to account for other local factors, such as local relative abuncances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, to better capture the strength of these mutualistic interactions at a macroecological scale.

We provide solid evidence for the generality of several hypothesized trait associations across a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and linked the reproductive spectrum with previously described fast-slow continuum' life-history strategies in plants {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animals {[}\protect\hyperlink{ref-healy2019}{64}{]}, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan. For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{20},\protect\hyperlink{ref-kettle2011}{21},\protect\hyperlink{ref-worley2000}{65}{]}, it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach. We found support to this trait association and show that other life history traits also covariate along this axis. Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{66}{]} by showing that most species with unisexual flowers \href{no\%20pillo\%20esto}{are concentrated in the trait space} and are associated with woody life forms with high flower number. Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{22}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors. Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays. Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.

Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales. For example, as predicted by \href{}{evolutionary? life-history?} theory, larger investments floral size and rewards to attract pollinators makes sense when pollinator dependence is higher, but this might trade off with the resources allocated to ovule production \href{Anne\%20Leonard\%20tenia\%20algo\%20de\%20eso,\%20creo}{mirate la literatura de esto\ldots{} seguro que hay papers. Además, si esto que digo l apoyan los datos, puede ser algo que la gente querra citar (YO QUIEREO!) asi que dejalo explicito}. Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings {[}\protect\hyperlink{ref-hegland2005}{67}--\protect\hyperlink{ref-kaiser2014}{69}{]}. Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes {[}\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{31},\protect\hyperlink{ref-faegri2013}{70}{]}. For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies \href{}{name which ones} and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{71},\protect\hyperlink{ref-foldesi2021}{72}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies. In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{73},\protect\hyperlink{ref-encinas2012}{74}{]} that reproductive correlations do not.

@@

\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
\CSLLeftMargin{67. }
\CSLRightInline{Hegland SJ, Totland Ø. 2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594. (doi:\href{https://doi.org/10.1007/s00442-005-0165-6}{10.1007/s00442-005-0165-6})}

\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
\CSLLeftMargin{68. }
\CSLRightInline{Lázaro A, Jakobsson A, Totland Ø. 2013 How do pollinator visitation rate and seed set relate to species' floral traits and community context? \emph{Oecologia} \textbf{173}, 881--893. (doi:\href{https://doi.org/10.1007/s00442-013-2652-5}{10.1007/s00442-013-2652-5})}

\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
\CSLLeftMargin{69. }
\CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J. 2014 Determinants of the microstructure of plant\textendash pollinator networks. \emph{Ecology} \textbf{95}, 3314--3324. (doi:\href{https://doi.org/10.1890/14-0024.1}{10.1890/14-0024.1})}

\leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
\CSLLeftMargin{70. }
\CSLRightInline{Faegri K, Van Der Pijl L. 2013 Principles of pollination ecology. }

\leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
\CSLLeftMargin{71. }
\CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D. 2020 Non-bee insects as visitors and pollinators of crops: Biology, ecology, and management. \emph{Annu. Rev. Entomol.} \textbf{65}, 391--407. (doi:\href{https://doi.org/10.1146/annurev-ento-011019-025055}{10.1146/annurev-ento-011019-025055})}

\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
\CSLLeftMargin{72. }
\CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P. 2021 Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis. \emph{J. Appl. Ecol.} \textbf{58}, 699--707. (doi:\href{https://doi.org/10.1111/1365-2664.13798}{10.1111/1365-2664.13798})}

\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
\CSLLeftMargin{73. }
\CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R. 2007 Species abundance and asymmetric interaction strength in ecological networks. \emph{Oikos} \textbf{116}, 1120--1127. (doi:\href{https://doi.org/10.1111/j.0030-1299.2007.15828.x}{10.1111/j.0030-1299.2007.15828.x})}

\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
\CSLLeftMargin{74. }
\CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS. 2012 Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208. (doi:\href{https://doi.org/10.1111/j.1461-0248.2011.01726.x}{10.1111/j.1461-0248.2011.01726.x})}

>>>>

The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalized degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, specialization \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03). Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization. On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a). However, specialization showed the opposite trend on this axis (figure S9g). On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c). Again, specialization showed the opposite trend to number of visits (figure S9i).

@@

The reproductive spectrum of flowering plants show clear positive and negative covariations between reproductive traits that shape the interactions of Angiosperms with their floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider only morphological and physiological traits {[}\protect\hyperlink{ref-diaz2016}{16},\protect\hyperlink{ref-carmona2021}{18}{]}, our results are consistent with the largest and most recent study that has characterised plant life strategies including reproductive and plant form and size related traits {[}\protect\hyperlink{ref-salguero2016}{7}{]}. Interestingly, the different plant reproductive axes were able to partly explain the number of interacting partners of different floral visitor guilds. However, they were insufficient to capture the visitation rates by guild or other species-level network metrics, which highlight the need to account for other local factors, such as species relative abuncances {[}\protect\hyperlink{ref-bartomeus2016}{33}{]}, to better understand the association of these mutualistic interactions at a macroecological scale.

Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1200 species) within a multitrait context and links the reproductive spectrum with the previously described fast-slow continuum' in plant {[}\protect\hyperlink{ref-salguero2016}{7}{]} and animal {[}\protect\hyperlink{ref-healy2019}{64}{]} life-history strategies, as indicated by the different reproductive traits associated with the traits of plant height, life form and lifespan. For instance, although the negative correlation between flower number and flower size has received substantial attention {[}\protect\hyperlink{ref-sargent2007}{20},\protect\hyperlink{ref-kettle2011}{21},\protect\hyperlink{ref-worley2000}{65}{]}, it has only been investigated across a few hundred of Angiosperm species with a pair-wise trait approach. We found support to this trait association and show that other life history traits also covariate along this axis. Our study also complements previous evidence that links breeding systems and life forms {[}\protect\hyperlink{ref-friedman2020}{8},\protect\hyperlink{ref-petit2006}{66}{]} by showing that most species with unisexual flowers are associated with woody life forms with high flower number. Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display {[}\protect\hyperlink{ref-goodwillie2010}{22}{]} where species with high pollinator dependence have greater allocation of resources to attract floral visitors. Despite floral rewards not being included in the main analysis because there was insufficient data available, both pollen and nectar quantity were clearly associated with plant species with larger floral displays. Our results highlight the presence of worldwide reproductive trait covariation patterns across flowering plants that are likely to impose constraints to the global spectrum of plant trait variation.

Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales. For example, as predicted by evolutionary life-history theory {[}\protect\hyperlink{ref-stebbins1970}{67}{]}, larger investments floral size and rewards to attract pollinators makes sense when pollinator dependence is higher, but this might trade off with the resources allocated to ovule production \href{Anne\%20Leonard\%20tenia\%20algo\%20de\%20eso,\%20creo}{mirate la literatura de esto\ldots{} seguro que hay papers. Además, si esto que digo l apoyan los datos, puede ser algo que la gente querra citar (YO QUIEREO!) asi que dejalo explicito}. Interestingly, by combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings {[}\protect\hyperlink{ref-hegland2005}{68}--\protect\hyperlink{ref-kaiser2014}{70}{]}. Because plants can adapt to the most efficient floral visitors {[}\protect\hyperlink{ref-fenster2004}{3}{]}, the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes {[}\protect\hyperlink{ref-dellinger2020}{4},\protect\hyperlink{ref-rosas2014}{31},\protect\hyperlink{ref-faegri2013}{71}{]}. For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies \href{}{name which ones} and because these two guilds are likely to differ in ecology and behaviour {[}\protect\hyperlink{ref-rader2020}{72},\protect\hyperlink{ref-foldesi2021}{73}{]} they may exert different selective pressures that lead to divergent plant reproductive strategies. In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability {[}\protect\hyperlink{ref-bartomeus2016}{33},\protect\hyperlink{ref-vazquez2007}{74},\protect\hyperlink{ref-encinas2012}{75}{]} that reproductive correlations do not.

@@

\leavevmode\vadjust pre{\hypertarget{ref-stebbins1970}{}}%
\CSLLeftMargin{67. }
\CSLRightInline{Stebbins GL. 1970 Adaptive radiation of reproductive characteristics in angiosperms, i: Pollination mechanisms. \emph{Annual Review of Ecology and Systematics}, 307--326. (doi:\href{https://doi.org/10.1146/annurev.es.01.110170.001515}{10.1146/annurev.es.01.110170.001515})}

\leavevmode\vadjust pre{\hypertarget{ref-hegland2005}{}}%
\CSLLeftMargin{68. }
\CSLRightInline{Hegland SJ, Totland Ø. 2005 Relationships between species' floral traits and pollinator visitation in a temperate grassland. \emph{Oecologia} \textbf{145}, 586--594. (doi:\href{https://doi.org/10.1007/s00442-005-0165-6}{10.1007/s00442-005-0165-6})}

\leavevmode\vadjust pre{\hypertarget{ref-lazaro2013}{}}%
\CSLLeftMargin{69. }
\CSLRightInline{Lázaro A, Jakobsson A, Totland Ø. 2013 How do pollinator visitation rate and seed set relate to species' floral traits and community context? \emph{Oecologia} \textbf{173}, 881--893. (doi:\href{https://doi.org/10.1007/s00442-013-2652-5}{10.1007/s00442-013-2652-5})}

\leavevmode\vadjust pre{\hypertarget{ref-kaiser2014}{}}%
\CSLLeftMargin{70. }
\CSLRightInline{Kaiser-Bunbury CN, Vázquez DP, Stang M, Ghazoul J. 2014 Determinants of the microstructure of plant\textendash pollinator networks. \emph{Ecology} \textbf{95}, 3314--3324. (doi:\href{https://doi.org/10.1890/14-0024.1}{10.1890/14-0024.1})}

\leavevmode\vadjust pre{\hypertarget{ref-faegri2013}{}}%
\CSLLeftMargin{71. }
\CSLRightInline{Faegri K, Van Der Pijl L. 2013 Principles of pollination ecology. }

\leavevmode\vadjust pre{\hypertarget{ref-rader2020}{}}%
\CSLLeftMargin{72. }
\CSLRightInline{Rader R, Cunningham S, Howlett B, Inouye D. 2020 Non-bee insects as visitors and pollinators of crops: Biology, ecology, and management. \emph{Annu. Rev. Entomol.} \textbf{65}, 391--407. (doi:\href{https://doi.org/10.1146/annurev-ento-011019-025055}{10.1146/annurev-ento-011019-025055})}

\leavevmode\vadjust pre{\hypertarget{ref-foldesi2021}{}}%
\CSLLeftMargin{73. }
\CSLRightInline{Földesi R, Howlett BG, Grass I, Batáry P. 2021 Larger pollinators deposit more pollen on stigmas across multiple plant species---a meta-analysis. \emph{J. Appl. Ecol.} \textbf{58}, 699--707. (doi:\href{https://doi.org/10.1111/1365-2664.13798}{10.1111/1365-2664.13798})}

\leavevmode\vadjust pre{\hypertarget{ref-vazquez2007}{}}%
\CSLLeftMargin{74. }
\CSLRightInline{Vázquez DP, Melián CJ, Williams NM, Blüthgen N, Krasnov BR, Poulin R. 2007 Species abundance and asymmetric interaction strength in ecological networks. \emph{Oikos} \textbf{116}, 1120--1127. (doi:\href{https://doi.org/10.1111/j.0030-1299.2007.15828.x}{10.1111/j.0030-1299.2007.15828.x})}

\leavevmode\vadjust pre{\hypertarget{ref-encinas2012}{}}%
\CSLLeftMargin{75. }
\CSLRightInline{Encinas-Viso F, Revilla TA, Etienne RS. 2012 Phenology drives mutualistic network structure and diversity. \emph{Ecol. Lett.} \textbf{15}, 198--208. (doi:\href{https://doi.org/10.1111/j.1461-0248.2011.01726.x}{10.1111/j.1461-0248.2011.01726.x})}

### 2022-07-07 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
edit

_Reproductive traits_

@@

-	Ovule number: We searched for the number of ovules per flower for all the different species. The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum. Many species were filled by genus or family level because the number of ovules in this taxonomic groups is considered to be mostly constant (e.g., Lamiaceae Boraginaceae or Apiaceae).

@@

-	Style length: The length of the style (mm) of the different species was also included. When possible, we calculated style length from images and illustrations on the online floras.

- Nectar provision: We recorded the presence and absence of nectar for all species. In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration. For species that did not have nectar information but belonged to a family that is considered as ‘nectarless’, this trait was recorded at family level and the species was recorded with ‘absence’ of nectar. This was done exclusively for well documented nectarless taxonomical groups. For the field of microlitres of nectar, we considered single measurements of nectar standing crop. In general terms, the timming of the measurement and methodology differed across studies. For instance, some studies measured nectar in freshly opened flowers while others in flowers that were bagged for 24 hours. Despite the different methodologies to measure nectar provision, we believe that this is an appropriate way to collate measurements of nectar to explore trait associations at a macroecological scale.

- Pollen grains per flower: We recorded pollen grains per flower for all species but this field was rarely described in the literature. When just the pollen:ovule ratio was found we converted it back to pollen grains by multiplying it by the average ovule number found for each species.

_Vegetative traits_

>>>>

_Reproductive biology traits_

@@

-	Ovule number: We searched for the number of ovules per flower for all the different species. The number of ovules of Asteraceae species are considered as the total number of ovules per capitulum. Many species were filled by genus or family level because the number of ovules of some taxonomic groups is considered to be mostly constant (e.g., Lamiaceae, Boraginaceae or Apiaceae).

@@

-	Style length: We searched for the length of the style (the pistil excluding the ovary and the stigma) in millimeters for all plant species. When the information about style length was missing, we tried to calculate it from images and illustrations from online resources (e.g., floras).

- Nectar provision: We recorded the presence and absence of nectar for all species. In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration. For species that did not have nectar information but belonged to a family that is considered as ‘nectarless’, this trait was recorded at family level and the species was recorded with ‘absence’ of nectar. This was done exclusively for well documented nectarless taxonomical groups. For the field of microlitres of nectar, we considered single measurements of nectar standing crop. Despite the timing and methodology of the different quantitative measurements of nectar differed across studies, these fields allowed us to have an approximate idea of the reproductive investment of the different plant species.

- Pollen grains per flower: For each species, we searched for the total number of pollen grains per flower. Because this fields was rarely available, we also tried to recover from pollen:ovule ratio information the total number of pollen grains by multiplying it by the average ovule number found for each species.

_Other life history traits_
